\begin{abstract}

Communicating data insights effectively to a general audience has become a fundamental problem in the information explosion era. We have seen a growing interest in telling data-driven stories to alleviate this issue. Specifically, these data-driven stories are structured by findings from data and often incorporate visual representations into the process of narration. However, crafting such visual data stories is non-trivial and time-consuming. Particularly, effective visual design in a data story remains underexplored. Besides, narrative authoring tools are still in the infancy and do not keep pace with innovation in practice. These gaps catalyze the growth of research interest in the visualization field. Existing studies have shown typical visual design in data-driven storytelling, taking an initial step to ease the creation process. They indicate the potential to easily produce high-quality data stories for communication. 


In this survey, we discuss the development of visual design in data-driven storytelling, as well as the authoring tools. The survey begins with an introduction to the motivation and challenges of data-driven storytelling. Then, based on the definition of the term \textit{narrative}, we review visual design in three primary story components, namely, scenes, sequences, and transitions, and discuss how they compose a visual data story. After that, we investigate existing authoring tools and reflect on evaluation methodologies. The survey ends with current research gaps and future directions in data-driven storytelling.




\end{abstract}
